---
title: "Ebola Outbreak"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    horizontal_layout: fill
    source_code: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(dplyr)
library(ggplot2)
library(plotly)

# Load my dataset
ebola <- readRDS("datasets/ebola_cleaned.rds")
```

# Sidebar {.sidebar}
You can also convert a page or a column into a “sidebar” on the left side of the dashboard by adding the {.sidebar} attribute. It can hold text (viewable from any page), or if you have integrated shiny interactivity it can be useful to hold user-input controls such as sliders or drop-down menus.

# Overview

This dashboard is produced for the leadership of Wakama County.
It aims to advise them on the status of the Ebola outbreak.


**There are `r format(nrow(ebola),big.mark=",", big.interval=3)` cases reported as hospitalized, as of `r max(ebola$date_hospitalisation, na.rm = T)`**

### Summary Data

#### Hospitalizations

``` {r hospital_data}
ebola %>%
  group_by(Hospital = hospital) %>%
  summarise(Cases = n()) %>%
  knitr::kable()
```

# Basic Stats

## Infections by Age {data-width=350}
```{r infect_age}
g <- ggplot(ebola, aes(age_cat)) +
  geom_bar(aes(fill=outcome)) 
  plotly::ggplotly(g)
```


## Epicurve {data-width=350}

```{r epicurve}
ggplot(ebola, aes(date_infection)) +
  geom_bar(aes(fill=gender))
```

# Health Indicators {data-navmenu="Indicators"}
Health Indicators

# Economic Indicators {data-navmenu="Indicators"}
Economic Indicators
