---
title: "Good old Iris"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
---

```{r setup, include=FALSE}
library(flexdashboard)
library(ggplot2)
library(dplyr)
# Read in data
data("iris")
```

## Row {data-height=100}
Iris is a flowering plant genus of 310 accepted species with showy flowers. As well as being the scientific name, iris is also widely used as a common name for all Iris species, as well as some belonging to other closely related genera.

## Row {data-height=300}
### Sample Size

```{r}
valueBox(value=nrow(iris),
         caption = "irises samples",
         icon = "fa-solid fa-snowflake",
         color = "pink")
```

### Short Irises

```{r}
short_setosa <- iris %>%
  filter(Petal.Length < mean(Petal.Length)) %>%
  nrow()
gauge(short_setosa, min=0, max=nrow(iris), symbol = "irises", 
      gaugeSectors(success = c(101,150), 
                   warning = c(51,100), 
                   danger = c(1,50)))
```

### Tall Irises

```{r}
short_setosa <- iris %>%
  filter(Petal.Length > mean(Petal.Length)) %>%
  nrow()
gauge(short_setosa, min=0, max=nrow(iris), symbol = "irises", 
      gaugeSectors(success = c(101,150), 
                   warning = c(51,100), 
                   danger = c(1,50)))
```

## Row {data-height=700}

### Species by Petal & Sepal values 

```{r}
ggplot(iris, aes(x=Petal.Length, y=Sepal.Width)) +
  geom_point(aes(color=Species))
```

### Sepal and petal averages

Below are the average Petal lengths and sepal widths for each iris species. 

```{r}
iris %>%
  group_by(Species) %>%
  summarise(Avg_SepalWidth = mean(Sepal.Width, na.rm = T),
            Avg_PetalLength = mean(Petal.Length, na.rm = T)) %>%
  knitr::kable()
```

